The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-08-17 paper.tex
wip

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage[]{algorithm2e}

@@

Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
interstellar medium (ISM). As photons from the CMB propagate through this intervening material,
scattering, absorption, or additional emission can perturb the thermal CMB spectrum. In order to
measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free emission,
thermal dust emission) are a nuisance and careful modeling and removal of these components is
essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.

@@

At redshifts $20 \gtrsim z \gtrsim 7$ the 21 cm hyperfine structure line of neutral hydrogen is
expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
2012RPPh...75h6901P}. The amplitude of this perturbation on a given line-of-sight is a function of
the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  The spatial
power spectrum of this perturbation is expected to be dominated by inhomogeneous heating of the IGM
at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim
7$ where a detection can constrain the ionizing efficiency of early galaxies, the UV photon
mean-free-path, and the minimum halo mass that can support star formation
\citep{2015MNRAS.449.4246G}.

@@

Just as for CMB experiments, foreground removal or suppression is an essential component of both
classes of 21 cm cosmology experiments. The brightness temperature of the galactic synchrotron
emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
\begin{equation}
    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.5}\,.
\end{equation}
Therefore experiments conservatively need to achieve at least 4 orders of dynamic range against this
foreground emission before the cosmological signal can be measured. Current foreground removal
methods (for example, \citealt{2012ApJ...756..165P}) rely on the assumption that the foreground
emission (after convolving with the instrumental response) is spectrally smooth. However the
low-frequency radio sky is composed of several components: galactic synchrotron emission, supernova
remnants, radio galaxies, free-free emission and absorption from \ion{H}{2} regions, and radion
emission from a confusing background of radio sources.  Ideally a foreground removal strategy should
be informed by the measured spatial structure and frequency spectrum of all foreground components.
However this possibility is limited by the availability of suitable high-fidelity low-frequency sky
maps on angular scales ranging from tens of degrees to arcminutes.

@@

Recently a host of new low-frequency sky surveys have been conducted including MSSS
\citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
\citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
catalog of radio point sources. Surveys that capture the diffuse emission include at 45 MHz, where
\citet{2011A&A...525A.138G} produced a map of the sky with 5$^\circ$ resolution, and the LWA1 Low
Frequency Sky Survey \citet{2017MNRAS.469.4537D}, which covers a range of frequencies between 35 MHz
and 80 MHz with resolution betwen 4.5$^\circ$ and 2$^\circ$.

@@

The goal of all imaging algorithms is to estimate the brightness of the sky $I_\nu(\hat r)$ in the
direction $\hat r$ and frequency $\nu$. A radio interferometer measures the visibilities
$V^{ij}_{\nu}$ between pairs of antennas -- here numbered $i$ and $j$ respectively. If the antennas
are separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes their response to the
incident radiation, then
\begin{equation}\label{eq:basic-imaging}
    V^{ij}_\nu = \int_\text{sky}
                 A_\nu(\hat r) I_\nu(\hat r)
                 \exp\bigg(2\pi i \hat r\cdot\vec b_{ij}/\lambda\bigg) \,\d\Omega \, .
\end{equation}
Imaging the output of a radio interferometer therefore consists of estimating $I_\nu(\hat r)$ given
the available measurements $V^{ij}_\nu$.

For later convenience we will define the baseline transfer function $B^{ij}_\nu(\hat r)$ such that
\begin{equation}\label{eq:baseline-transfer-function}
    V^{ij}_\nu = \int_\text{sky} B^{ij}_\nu(\hat r) I_\nu(\hat r) \,\d\Omega \, .
\end{equation}
The baseline transfer function defines the response of a single baseline to the sky, and is a
function of the antenna primary beam and baseline orientation.

Naively one might attempt to solve Equation~\ref{eq:basic-imaging} by discretizing, and subsequently
solving the resulting matrix equation. If the interferometer is composed of $N_\text{base}$
baselines, and measures $N_\text{freq}$ frequency channels over $N_\text{time}$ integrations then
the entire data set consists of $N_\text{base}N_\text{freq}N_\text{time}$ complex numbers. If the
sky is discretized into $N_\text{pix}$ pixels then the relevant matrix has dimensions of
$(N_\text{base}N_\text{freq}N_\text{time})\times(N_\text{pix})$. For making single-channel maps with
the OVRO-LWA this becomes a 5 petabyte array (assuming each matrix element is a 64-bit complex
floating point number).  This matrix equation is therefore prohibitively large, and solving
Equation~\ref{eq:basic-imaging} by means of discretization is usually impossible although
\citet{2017MNRAS.465.2901Z} demonstrate this technique with the MITEOR telescope.

@@

It can be shown that there is a discrete linear relationship between the $m$-modes $V^{ij}_{m,\nu}$
and the spherical harmonic coefficients of the sky brightness $a_{lm,\nu}$.
\begin{equation}\label{eq:m-mode-sum-equation}
    V^{ij}_{m,\nu} = \sum_l B^{ij}_{lm,\nu} a_{lm,\nu}\,,
\end{equation}
where the transfer coefficients $B^{ij}_{lm,\nu}$ define the interferometer's response to the sky.
For example, the transfer coefficients are a function of the baseline and antenna primary beam
pattern.

Equation~\ref{eq:m-mode-sum-equation} can be recognized as a matrix equation where the transfer
matrix $\b B$ is block-diagonal.
\begin{equation}
    \b B = \left(\begin{array}{cccc}
        m = 0 &&& \\
              & m=\pm1 && \\
              && m=\pm2 & \\
              &&& \ddots \\
    \end{array}\right)
\end{equation}
The vector $\b v$ contains the list of $m$-modes and the vector $\b a$ contains the list of
spherical harmonic coefficients representing the sky brightness. In order to take advantage of the
block-diagonal structure in $\b B$, $\b v$ and $\b a$ must be sorted by the value of $m$. Positive
and negative values of $m$ are grouped together because the brightness of the sky is real-valued,
and the spherical harmonic transform of a real-valued function has $a_{l(-m)} = (-1)^m a_{lm}^*$.
\begin{equation}\label{eq:m-mode-matrix-equation}
    \overbrace{\left(
        \begin{array}{c}
            \vdots \\
            m\text{-modes} \\
            \vdots \\
        \end{array}
    \right)}^{\b v}
    =
    \overbrace{\left(
        \begin{array}{ccc}
            \ddots & & \\
            & \text{transfer matrix} & \\
            & & \ddots \\
        \end{array}
    \right)}^{\b B}
    \overbrace{\left(
        \begin{array}{c}
            \vdots \\
            a_{lm} \\
            \vdots \\
        \end{array}
    \right)}^{\b a}
\end{equation}

@@

The interferometer's sensitivity to $l=0$, however, deserves special consideration.
\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that an interferometer is
only sensitive to the monopole of the sky brightness if there exists some form of cross-talk or
common-mode noise. In fact, the sensitivity of the interferometer is proportional to the amplitude
of these effects. For consistency we will include $a_{00}$ while solving
Equation~\ref{eq:m-mode-matrix-equation} for the vector $\b a$, but we set $a_{00} = 0$ afterwards
because we do not have a measurement of the amplitude of cross-talk or common-mode noise, which
would be needed to correctly calibrate $a_{00}$.

The size of a typical block in the transfer matrix is
$(2N_\text{base}N_\text{freq})\times(l_\text{max})$. If each element of the matrix is stored as a
64-bit complex floating point number, a single block is 500 MB for the case of single-channel
imaging with the OVRO-LWA. Compare this number with the 5 PB required for the naive approach.  The
power of $m$-mode analysis is the block-diagonal structure of
Equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
the computational complexity involved in inverting the equation is reduced by a factor $N^3$. For
the case of the OVRO-LWA the equation breaks up into $\sim10^3$ blocks and so we save a factor of
$\sim10^9$ in processing time by using $m$-mode analysis.

@@

\begin{figure}[t]
    \plotone{figures/lcurve/lcurve}
    \caption{
        An example L-curve using OVRO-LWA data at 36.528 MHz. The $x$-axis is the norm of the
        solution (in this case the spherical harmonic coefficients) given in arbitrary units. The
        $y$-axis is the least-squares norm given in arbitrary units. $\varepsilon$ is the
        regularization parameter. When the regularization parameter is small, the norm of the
        solution grows rapidly. When the regularization parameter is large, the least-squares norm
        grows rapidly. The optimal value for the regularization parameter is near
        $\varepsilon=0.01$.
    }
    \label{fig:lcurve}
\end{figure}

@@

$m$-mode analysis imaging automatically deconvolves angular scales described by modes for which the
singular values of $\b B$ are $\gg \sqrt{\varepsilon}$. For example, structures on angular scales
smaller than $\lambda/b_\text{min}$ and larger than $\lambda/b_\text{max}$ (where $b_\text{min}$ and
$b_\text{max}$ are the minimum and maximum baseline lengths) are generally well-measured by the
interferometer and will be automatically deconvolved during the imaging process. However, as the
total integration time of the data set increases, the noise in the data decreases. One consequence
of this is that the regularization parameter $\varepsilon$ can be decreased. This increases the
number of modes for which $\sigma_i \gg \sqrt{\varepsilon}$, and as a consequence the automatic
deconvolution can extend to scales larger than $\lambda/b_\text{min}$ and smaller than
$\lambda/b_\text{max}$.

However point sources do not get deconvolved by the imaging process even in the limit of infinite
SNR and $\varepsilon \rightarrow 0$. This is because point sources carry power to large values of
$l$ and by computational necessity we truncated the spherical harmonic representation of the sky at
some $l_\text{max}$. A consequence of this is that point sources will appear in the maps with a
characteristic point spread function (PSF). The PSF may be computed with:
\begin{equation}
    \b a_\text{PSF}(\theta, \phi)
        = (\b B^*\b B + \varepsilon\b I)^{-1}\b B^*\b B\b a_\text{PS}(\theta, \phi)\,,
\end{equation}
where $\b a_\text{PSF}(\theta, \phi)$ is the vector of spherical harmonic coefficients representing
the PSF at the spherical coordinates $(\theta, \phi)$, and $\b a_\text{PS}(\theta, \phi)$ is the
vector of spherical harmonic coefficients for a point source at $(\theta, \phi)$ given by
\begin{equation}
    a_{lm, \text{PS}}(\theta, \phi) = Y_{lm}^*(\theta, \phi)\,.
\end{equation}

In general the PSF can be a function of the right ascension and declination. However point sources
at the same declination take the same track through the sky and therefore (barring any ionospheric
effects) will have the same PSF. The PSF is actually only a function of the declination. For
example, sources at low elevations will tend to have an extended PSF along the north-south axis due
to baseline foreshortening. An example computed PSF is shown in Figure~\ref{fig:psf}.

The computed PSF as a function of frequency and declination can be used to adapt the CLEAN algorithm
\citep{1974A&AS...15..417H} to $m$-mode analysis.

\begin{algorithm}
    \KwData{dirty maps generated from the output of Equation~\ref{eq:tikhonov-solution};}
    \KwResult{clean maps with point sources deconvolved;}
    pre-compute $\b M = (\b B^*\b B + \varepsilon\b I)^{-1}\b B^*\b B$\;
    \While{noise in map $>$ threshold}{
        identify the pixel with the largest amplitude\;
        compute $\b a_\text{PSF} = \b M \b a_\text{PS}$\;
        update $\b a \leftarrow \b a - (\textit{gain})\times\b a_\text{PSF}$\;
    }
    convolve removed components with a CLEAN-beam and restore to the map\;
\end{algorithm}

It should be noted that for interferometers with more baselines than the number of spherical
harmonics used in the maps, $\b M$ is a much smaller matrix than the full transfer matrix $\b B$.
Therefore the cost of multiplying by $\b M$ can actually be dominated by the cost of computing the
spherical harmonics describing a point source at the identified pixel.

@@

\begin{figure}[ht]
    \plotone{figures/antenna-layout/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
        antennas equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

\begin{figure}[ht]
    \plotone{figures/psf/spw04-psf-45-degrees}
    \caption{
        The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
        declination of $+45^\circ$ and frequency of $36.528$ MHz.
    }
    \label{fig:psf}
\end{figure}

@@

\begin{figure*}[ht]
    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
    \caption{
        (left panel) The tracks traced through the sky by the 8 brightest point sources visible to the
        OVRO-LWA.
        (right panel) The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
    }
    \label{fig:beam}
\end{figure*}

@@

%\todo{slice through Cyg A and Cas A to illustrate the removal process}
%\todo{Give a plot with the updated source models}

@@

\begin{figure*}[ht]
    \includegraphics[width=\textwidth]{figures/flux-scale/flux-scale}
    \caption{
        This figure shows the measured fluxes (black points) of 11 sources plotted against the
        published spectra from \citet{2017ApJS..230....7P} (solid line above 50 MHz, dotted line
        below 50 MHz), \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B}
        (dot-dash line).
    }
    \label{fig:flux-scale}
\end{figure*}

@@

\begin{table*}[ht]
    \centering
    \begin{tabular}{cccccc}
        \hline
        \hline
        & \tbf{Frequency} & \tbf{Bandwidth} & \tbf{FWHM} & \multicolumn2c{\tbf{Thermal Noise}} \\
        \cline{5-6}
        \tbf{\#} & (MHz)  & (MHz)          & (arcmin)  & (K) & (Jy) \\
        \hline
        1 & 36.528 & 0.024 & 16.2 & 372.8 & \\
        2 & 41.760 & 0.024 & 14.7 & 321.2 & \\
        3 & 46.992 & 0.024 & 14.2 & 247.0 & \\
        4 & 52.224 & 0.024 & 13.6 & 205.7 & \\
        5 & 57.456 & 0.024 & 13.5 & 167.7 & \\
        6 & 62.688 & 0.024 & 13.5 & 137.6 & \\
        7 & 67.920 & 0.024 & 13.5 & 114.9 & \\
        8 & 73.152 & 0.024 & 13.7 &  93.4 & \\
        \hline \hline
    \end{tabular}
    \caption{Summary of the generated all-sky maps\label{tab:summary}}
\end{table*}

@@

%\todo{text}

@@

%\todo{compute B*v for panels (c) and (d) to show that the pick-up is pretty bad. my expectation is
%that it is actually worse than the RFI, but I don't actually know for sure}

@@

%\todo{describe how the Wiener filter works}

@@

%\todo{discuss the possibility of declination dependent flux-scale errors in these maps}

@@

%\todo{quick simulation of this?}

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\newcommand*\Let[2]{\State #1 $\gets$ #2}
\algrenewcommand\algorithmicrequire{\textbf{Precondition:}}
\algrenewcommand\algorithmicensure{\textbf{Postcondition:}}

@@

Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
interstellar medium (ISM). As photons from the CMB propagate through this intervening material,
scattering, absorption, or additional emission can perturb or corrupt the thermal CMB spectrum. In
order to measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free
emission, thermal dust emission) are a nuisance and careful modeling and removal of these components
is essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.

@@

At redshifts $20 \gtrsim z \gtrsim 7$ the 21 cm hyperfine structure line of neutral hydrogen is
expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
2012RPPh...75h6901P}. The amplitude of this perturbation on a given line-of-sight is a function of
the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  The spatial
power spectrum of this perturbation is thought to be dominated by inhomogeneous heating of the IGM
at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim
7$ where a detection can constrain the ionizing efficiency of early galaxies, the UV photon
mean-free-path, and the minimum halo mass that can support star formation
\citep{2015MNRAS.449.4246G}.

@@

Just as for CMB experiments, foreground removal or suppression is an essential component of both
classes of 21 cm cosmology experiments. The brightness temperature of the galactic synchrotron
emission at high galactic latitudes is measured by \citet{2008AJ....136..641R} as
\begin{equation}
    T \sim 300\,{\rm K} \times \left(\frac{\nu}{150\,{\rm MHz}}\right)^{-2.5}\,.
\end{equation}
Therefore experiments conservatively need to achieve at least 4 orders of dynamic range against this
foreground emission before the cosmological signal can be measured. Current foreground removal
methods (for example, \citealt{2012ApJ...756..165P}) rely on the assumption that the foreground
emission (after convolving with the instrumental response) is spectrally smooth. However the
low-frequency radio sky is composed of several components: galactic synchrotron emission, supernova
remnants, radio galaxies, free-free emission and absorption from \ion{H}{2} regions, and a confusing
background of radio sources.  Ideally a foreground removal strategy should be informed by the
measured spatial structure and frequency spectrum of all foreground components.  However this
possibility is limited by the availability of suitable high-fidelity low-frequency sky maps on
angular scales ranging from tens of degrees to arcminutes.

@@

Recently a host of new low-frequency sky surveys have been conducted including MSSS
\citep{2015A&A...582A.123H}, GLEAM \citep{2015PASA...32...25W}, and TGSS
\citep{2017A&A...598A..78I}. However, the primary data product generated by these surveys is a
catalog of radio point sources. Surveys that capture the diffuse emission include at 45 MHz, where
\citet{2011A&A...525A.138G} produced a map of the sky with 5$^\circ$ resolution, and the LWA1 Low
Frequency Sky Survey \citep{2017MNRAS.469.4537D}, which covers a range of frequencies between 35 MHz
and 80 MHz with resolution betwen 4.5$^\circ$ and 2$^\circ$.

@@

The goal of all imaging algorithms is to estimate the brightness of the sky $I_\nu(\hat r)$ in the
direction $\hat r$ and frequency $\nu$. A radio interferometer measures the visibilities
$V^{ij}_{\nu}$ between pairs of antennas -- here numbered $i$ and $j$ respectively. If the antennas
are separated by the baseline $\vec b_{ij}$, and $A_\nu(\hat r)$ describes their response to the
incident radiation, then
\begin{equation}\label{eq:basic-imaging}
    V^{ij}_\nu = \int_\text{sky}
                 A_\nu(\hat r) I_\nu(\hat r)
                 \exp\bigg(2\pi i \hat r\cdot\vec b_{ij}/\lambda\bigg) \,\d\Omega \, .
\end{equation}
Constructing an image from the output of a radio interferometer therefore consists of estimating
$I_\nu(\hat r)$ given the available measurements $V^{ij}_\nu$.

For later convenience we will define the baseline transfer function $B^{ij}_\nu(\hat r)$ such that
\begin{equation}\label{eq:baseline-transfer-function}
    V^{ij}_\nu = \int_\text{sky} B^{ij}_\nu(\hat r) I_\nu(\hat r) \,\d\Omega \, .
\end{equation}
The baseline transfer function defines the response of a single baseline to the sky, and is a
function of the antenna primary beam, and baseline length and orientation.

Naively one might attempt to solve Equation~\ref{eq:basic-imaging} by discretizing, and subsequently
solving the resulting matrix equation. If the interferometer is composed of $N_\text{base}$
baselines, and measures $N_\text{freq}$ frequency channels over $N_\text{time}$ integrations, then
the entire data set consists of $N_\text{base}N_\text{freq}N_\text{time}$ complex numbers. If the
sky is discretized into $N_\text{pix}$ pixels then the relevant matrix has dimensions of
$(N_\text{base}N_\text{freq}N_\text{time})\times(N_\text{pix})$. For making single-channel maps with
the OVRO-LWA this becomes a 5 petabyte array (assuming each matrix element is a 64-bit complex
floating point number).  This matrix equation is therefore prohibitively large, and solving
Equation~\ref{eq:basic-imaging} by means of discretization is usually impossible although
\citet{2017MNRAS.465.2901Z} demonstrate this technique with the MITEOR telescope.

@@

It can be shown that there is a discrete linear relationship between the measured $m$-modes
$V^{ij}_{m,\nu}$ and the spherical harmonic coefficients of the sky brightness $a_{lm,\nu}$.
\begin{equation}\label{eq:m-mode-sum-equation}
    V^{ij}_{m,\nu} = \sum_l B^{ij}_{lm,\nu} a_{lm,\nu}\,,
\end{equation}
where the transfer coefficients $B^{ij}_{lm,\nu}$ define the interferometer's response to the sky.
These transfer coefficients are computed from the spherical harmonic transform of the baseline
transfer function defined by Equation~\ref{eq:baseline-transfer-function}.

Equation~\ref{eq:m-mode-sum-equation} can be recognized as a matrix equation where the transfer
matrix $\b B$ is block-diagonal.
\begin{equation}\label{eq:m-mode-matrix-equation}
    \overbrace{\left(
        \begin{array}{c}
            \vdots \\
            m\text{-modes} \\
            \vdots \\
        \end{array}
    \right)}^{\b v}
    =
    \overbrace{\left(
        \begin{array}{ccc}
            \ddots & & \\
            & \text{transfer matrix} & \\
            & & \ddots \\
        \end{array}
    \right)}^{\b B}
    \overbrace{\left(
        \begin{array}{c}
            \vdots \\
            a_{lm} \\
            \vdots \\
        \end{array}
    \right)}^{\b a}
\end{equation}
\begin{equation}
    \b B = \left(\begin{array}{cccc}
        m = 0 &&& \\
              & m=\pm1 && \\
              && m=\pm2 & \\
              &&& \ddots \\
    \end{array}\right)
\end{equation}
The vector $\b v$ contains the list of $m$-modes and the vector $\b a$ contains the list of
spherical harmonic coefficients representing the sky brightness. In order to take advantage of the
block-diagonal structure in $\b B$, $\b v$ and $\b a$ must be sorted by the absolute value of $m$.
Positive and negative values of $m$ are grouped together because the brightness of the sky is
real-valued, and the spherical harmonic transform of a real-valued function has $a_{l(-m)} = (-1)^m
a_{lm}^*$.

@@

The interferometer's sensitivity to the monopole ($a_{00}$) deserves special consideration.
\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that a baseline with
nonzero sensitivity to $a_{00}$ must also have some amount of cross-talk or common-mode noise.  In
fact the sensitivity to $a_{00}$ is proportional to a sum of these effects. For example, one way a
baseline can have nonzero sensitivity to $a_{00}$ is if the baseline is extremely short. In this
case the antennas are so close together that voltage fluctuations in one antenna can couple into the
other antenna. In order to make an interferometric measurement of $a_{00}$, this coupling must be
measured and calibrated.

The size of a typical block in the transfer matrix is
$(2N_\text{base}N_\text{freq})\times(l_\text{max})$. If each element of the matrix is stored as a
64-bit complex floating point number, a single block is 500 MB for the case of single-channel
imaging with the OVRO-LWA. Compare this number with the 5 PB required for the naive approach.  The
power of $m$-mode analysis is the block-diagonal structure of
Equation~\ref{eq:m-mode-matrix-equation}.  By breaking up the problem into $N$ independent blocks,
the computational complexity involved in inverting a single block is reduced by a factor of $N^3$
relative to a dense matrix. However we must invert $N$ blocks, so the overall computational savings
is proportional to $N^2$.  For the case of the OVRO-LWA the equation breaks up into $\sim10^3$
blocks and so we save a factor of $\sim10^6$ in processing time by using $m$-mode analysis.

@@

\begin{figure}[t]
    \plotone{figures/lcurve/lcurve}
    \caption{
        An example L-curve using OVRO-LWA data at 36.528 MHz. The $x$-axis is the norm of the
        solution (in this case the spherical harmonic coefficients) given in arbitrary units. The
        $y$-axis is the least-squares norm given in arbitrary units. $\varepsilon$ is the
        regularization parameter. When the regularization parameter is small, the norm of the
        solution grows rapidly. When the regularization parameter is large, the least-squares norm
        grows rapidly.
    }
    \label{fig:lcurve}
\end{figure}

@@

In traditional radio astronomy imaging, the CLEAN algorithm \citep{1974A&AS...15..417H} is used to
interpolate the measured visibilities onto the $uv$-plane. In the absence of this interpolation,
gaps in the interferometer's $uv$-coverage are assumed to be zero, and in the image plane sources
are convolved with a point spread function (PSF) that is characteristic of the $uv$-coverage.
Fundamentally, the interferometer's PSF in the dirty images is determined by which modes were
assumed to be zero in the initial imaging process.

In $m$-mode analysis imaging, we assumed modes were zero in two separate ways:
\begin{enumerate}
    \item We selected a set of spherical harmonic coefficients $a_{lm}$ to describe the sky
        brightness distribution. All modes with $l>l_\text{max}$ are neglected and assumed to be
        zero.
    \item Tikhonov regularization forces linear combinations of spherical harmonic coefficients with
        $\sigma_i \lesssim \sqrt{\varepsilon}$ towards zero.
\end{enumerate}
As a consequence the final map of the sky is not assembled from a complete set of spherical
harmonics. Therefore just as in traditional imaging, $m$-mode analysis imaging produces dirty maps
where sources are convolved with a PSF.  This PSF can be improved by increasing the number and
variety of baselines, which increases the number of modes where $\sigma_i \gg \sqrt{\varepsilon}$.
Alternatively by collecting more data, the signal-noise ratio of the measured $m$-modes increases,
which allows the observer to lower the value of $\varepsilon$ without increasing the noise in the
maps.  Finally, the CLEAN algorithm can be applied to interpolate some of the missing information
that was assumed to be zero.

The PSF of a dirty $m$-mode analysis map may be computed with
\begin{equation}\label{eq:psf}
    \b a_\text{PSF}(\theta, \phi)
        = (\b B^*\b B + \varepsilon\b I)^{-1}\b B^*\b B\b a_\text{PS}(\theta, \phi)\,,
\end{equation}
where $\b a_\text{PSF}(\theta, \phi)$ is the vector of spherical harmonic coefficients representing
the PSF at the spherical coordinates $(\theta, \phi)$, and $\b a_\text{PS}(\theta, \phi)$ is the
vector of spherical harmonic coefficients for a point source at $(\theta, \phi)$ given by
\begin{equation}
    \b a_\text{PS}(\theta, \phi) = \begin{pmatrix}
        \vdots \\
        Y_{lm}^*(\theta, \phi) \\
        \vdots \\
    \end{pmatrix}
    = \begin{pmatrix}
        \vdots \\
        Y_{lm}^*(\theta, 0)\times e^{im\phi} \\
        \vdots \\
    \end{pmatrix} \,.
\end{equation}
In general the PSF can be a function of the right ascension and declination. However point sources
at the same declination take the same track through the sky and therefore (barring any ionospheric
effects) will have the same PSF. The PSF is therefore only a function of the declination. For
example, sources at low elevations will tend to have an extended PSF along the north-south axis due
to baseline foreshortening. An example computed PSF is shown in Figure~\ref{fig:psf}.  Adapting
CLEAN for $m$-mode analysis requires either pre-computing Equation~\ref{eq:psf} at a grid of
declinations, or a method for rapidly evaluating Equation~\ref{eq:psf} on the fly.

\todo{cite lincoln's paper on cleaning with a changing psf}

For an interferometer with more baselines than spherical harmonics used in the maps (eg. the
OVRO-LWA), $\b B^*\b B$ can be a much smaller matrix than the full transfer matrix $\b B$. Therefore
pre-computing $\b B^*\b B$ can allow the entire matrix to fit into memory on a single machine. This
greatly reduces the amount of disk I/O necessary for solving Equation~\ref{eq:psf}.

Additionally we can pre-compute the Cholesky decomposition of $\b B^*\b B + \varepsilon\b I = \b
U^*\b U$, where $\b U$ is an upper-triangular matrix. Inverting an upper triangular matrix is an
$\mathcal{O}(N^2)$ operation (instead of $\mathcal{O}(N^3)$ for a general matrix inverse).\footnote{
    Inverting a matrix is numerically unstable and should be avoided. Instead of computing $\b
    U^{-1}$, the linear equation $\b U\b x = \b y$ is solved each time the matrix inverse is needed.
}
Equation~\ref{eq:psf} can then be rapidly evaluated from right to left as:
\begin{equation}\label{eq:rapid-psf}
    \b a_\text{PSF} =
        \b U^{-1}\,\big(\b U^*\big)^{-1}\,\big(\b B^*\b B\big)\,\b a_\text{PS}\,.
\end{equation}
Furthermore, Equation~\ref{eq:rapid-psf} does not need to be separately evaluated for each CLEAN
component. Instead we can identify $N$ CLEAN components, accumulate $\b a_\text{PS}$ for each
component, and evaluate Equation~\ref{eq:rapid-psf} on the accumulation. This can greatly reduce the
number of times this equation needs to be evaluated, but care must be taken to ensure that the $N$
components are not so close together that sidelobes from one may interact with another.

\todo{describe blurring to avoid cleaning the diffuse emission}

Altogether the adaptation of CLEAN applied to the maps presented in this paper is summarized below.
\begin{algorithmic}[1]
    \Require{$\b a$ is the solution to Equation~\ref{eq:tikhonov-solution}}
    \Function{CLEAN}{$\b a$}
    \Let{$\b M$}{$\b B^*\b B^*$}
    \Let{$\b U$}{${\rm chol}(\b B)$} \Comment{Cholesky decomposition}
    \While{noise in map $>$ threshold}
    \State find $N$ pixels with the largest residual flux
    \Let{$\b x$}{$\sum_{i=1}^N \,(\text{pixel flux}) \times \b a_\text{PS}(\theta_i, \phi_i)$}
    \Let{$\b y$}{$\b U^{-1}\big(\b U^*\big)^{-1}\b M\b x$}
    \Let{$\b a$}{$\b a - (\text{loop gain})\times\b y$}
    \State record subtracted components
    \EndWhile
    \Let{$\b a$}{$\b a + (\text{restored components})$}
    \State \Return{$\b a$}
    \EndFunction
\end{algorithmic}

@@

\begin{figure}[t]
    \plotone{figures/antenna-layout/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
        antennas equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

\begin{figure}[t]
    \plotone{figures/psf/spw04-psf-45-degrees}
    \caption{
        The computed $m$-mode analysis imaging PSF for the OVRO-LWA for a point source at a
        declination of $+45^\circ$ and frequency of $36.528$ MHz.
    }
    \label{fig:psf}
\end{figure}

@@

\begin{figure*}[t]
    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
    \caption{
        (left panel) The tracks traced through the sky by the 8 brightest point sources visible to the
        OVRO-LWA.
        (right panel) The amplitude of the OVRO-LWA beam at 36.528 MHz as a result of the beam model
        fit using Zernike polynomials and the symmetry assumptions outlined in the text.
    }
    \label{fig:beam}
\end{figure*}

@@

\todo{slice through Cyg A and Cas A to illustrate the removal process}

\todo{Give a plot with the updated source models}

@@

\begin{figure*}[t]
    \includegraphics[width=\textwidth]{figures/flux-scale/flux-scale}
    \caption{
        This figure shows the measured fluxes (black points) of 11 sources plotted against the
        published spectra from \citet{2017ApJS..230....7P} (solid line above 50 MHz, dotted line
        below 50 MHz), \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B}
        (dot-dash line).
    }
    \label{fig:flux-scale}
\end{figure*}

@@

\begin{table*}[t]
    \centering
    \begin{tabular}{cccccccccc}
        \hline
        \hline
        & \tbf{Frequency} & \tbf{Bandwidth} & \tbf{FWHM} &
            \multicolumn2c{\tbf{Thermal Noise}} &&
            \multicolumn2c{\tbf{Spherical Harmonics}} &
            \tbf{Singular Values} \\
        \cline{5-6}
        \cline{8-9}
        \tbf{\#} & MHz & MHz & arcmin &
            K & Jy &&
            $l=0$ & $m=0$ &
            fraction $>\sqrt{\varepsilon}$ \\
        \hline
        1 & 36.528 & 0.024 & 16.2 & 372.8 & & & no & yes \\
        2 & 41.760 & 0.024 & 14.7 & 321.2 & & & no & yes \\
        3 & 46.992 & 0.024 & 14.2 & 247.0 & & & no & no \\
        4 & 52.224 & 0.024 & 13.6 & 205.7 & & & no & no \\
        5 & 57.456 & 0.024 & 13.5 & 167.7 & & & no & no \\
        6 & 62.688 & 0.024 & 13.5 & 137.6 & & & no & no \\
        7 & 67.920 & 0.024 & 13.5 & 114.9 & & & no & no \\
        8 & 73.152 & 0.024 & 13.7 &  93.4 & & & no & no \\
        \hline \hline
    \end{tabular}
    \caption{Summary of the generated all-sky maps\label{tab:summary}}
\end{table*}

@@

\todo{text}

@@

\todo{compute B*v for panels (c) and (d) to show that the pick-up is pretty bad. my expectation is
that it is actually worse than the RFI, but I don't actually know for sure}

@@

\todo{describe how the Wiener filter works}

@@

\todo{discuss the possibility of declination dependent flux-scale errors in these maps}

@@

\todo{quick simulation of this?}
